AP/PA Tables ITHIM Global

### 2023-05-12 summary_tables_PA_AP.Rmd
Move back rmd docs to the root
updated input file and corrected ouput file path
Regen rmd docs
Update result/docs for v20. Previous relevant commit: 37b8f5d43690b0e0aa1e859b73caf245d1958aef
Regen using v23 InputParams
Update rmd docs for v24
Use v28 input params

input_parameter_file <- "InputParameters_v15.0.xlsx"
# scenario definition
scenario_name <- "GLOBAL"
reference_scenario <- 'Baseline'

@@

<!-- # Descriptive tables of emission inventory -->

<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->

<!-- trans_share<-c(22.5, 40.0, 22.5, 28.1)  -->
<!-- pm_conc<- c(50, 18, 122, 47 ) -->
<!-- city<-cities -->
<!-- shares<- as.data.frame(cbind(city,as.numeric(trans_share), pm_conc)) -->
<!-- names(shares)[2]<- "trans_share" -->
<!-- for (x in 1:length(cities)) -->
<!-- { -->
<!--   modes<-names(unlist(io[[cities[x]]]$emission_inventory)) -->
<!--   emissions<-as.data.frame(unlist(io[[cities[x]]]$emission_inventory)) -->
<!--   city_emissions<-cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$emission_inventory)`)) -->
<!--   names(city_emissions)[2]<- "emissions" -->
<!--   select<- c("car", "motorcycle", "bus_driver", "truck", "big_truck") -->
<!--   city_emissions$modes<- as.character(city_emissions$modes) -->
<!--   city_emissions$modes[!(city_emissions$modes %in% select)]<- "other" -->
<!--   summary<-city_emissions %>% group_by(modes) %>% summarise(sum(emissions)) -->
<!--   names(summary)[2]<- "emissions" -->
<!--   summary$emissions <- round(summary$emissions*100/sum(summary$emissions), digits=1) -->
<!--   summary<-as.data.frame(summary) -->
<!--   summary[nrow(summary)+1,1]<-"Transport share" -->
<!--   summary[nrow(summary),2]<-as.character(shares$trans_share[x]) -->
<!--   summary[nrow(summary)+1,1]<-"PM2.5 Conc" -->
<!--   summary[nrow(summary),2]<-as.character(shares$pm_conc[x]) -->
<!--   print(kable(summary, caption= cities[x])) -->

<!-- } -->

<!-- ``` -->

@@

# summary_all<- cbind(io[[cities[1]]]$summary_emission,io[[cities[2]]]$summary_emission,io[[cities[3]]]$summary_emission,io[[cities[4]]]$summary_emission)
# summary_all<- summary_all[-c(3,5,7)]
# summary_all$modes[2]<- "bus"
# 
# 
print(kable(sl))
```

@@

#cl$Scenario <- c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")
co2_conc$Scenario <- scen_names

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  #names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")
  #
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets)
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - 4):n_col] <- scen_names

@@

<!-- # Descriptive tables of injury outcomes -->

<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->
<!-- for (x in 1: length(cities)) -->
<!-- { -->

<!--   summary<- as.data.frame(io[[cities[x]]]$outcomes$injuries %>% group_by(scenario) %>% summarise('Ped'=sum(pedestrian,na.rm=T),'Bike'= sum(cycle), 'Car'=sum(car), "Motorcycle"=sum(motorcycle,na.rm=T), "All modes"=sum(Deaths,na.rm=T))) -->
<!--   summary$scenario<- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen") -->
<!--   summary<- cbind(summary$scenario ,round(summary[,2:6], digits=0)) -->
<!--   names(summary)[1]<-"Scenario" -->
<!--   print(kable(summary, caption= cities[x])) -->

<!-- } -->
<!-- ``` -->

<!-- # Striking vehicles in scenarios -->

<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->
<!-- for (x in 1: length(cities)) -->
<!-- { -->

<!-- scenarios<- c('Baseline', 'Scenario 1', 'Scenario 2', 'Scenario 3', 'Scenario 4', 'Scenario 5') -->
<!-- for (i in 1: length(scenarios)) -->
<!-- { -->
<!-- whw<-as.data.frame(rowSums(io[[cities[x]]]$outcomes$whw[[scenarios[i]]]$whw)) -->
<!-- noov<-as.data.frame(sum(io[[cities[x]]]$outcomes$whw[[scenarios[i]]]$nov)) -->
<!-- names(whw)[1]<- as.character(scenarios[i]) -->
<!-- names(noov)[1]<-as.character(scenarios[i]) -->

<!-- if (i ==1 ) -->
<!-- { -->
<!--  summary<-round(rbind(whw,nov=noov), digits = 1) -->
<!-- }  -->
<!-- else -->
<!-- { -->
<!-- summary<- cbind(summary, round(rbind(whw, nov=noov), digits=1) )  -->
<!-- } -->

<!-- } -->

<!-- names(summary)<-c("base", "walk", "bike", "car", "MC", "bus") -->
<!-- print(kable(summary, caption= cities[x])) -->

<!-- } -->

<!-- ``` -->

<!-- # Distance share by scenarios in percentages (excludes city-specific minority modes-- auto rickshaws, subway, etc.) -->

<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->
<!-- for (x in 1: length(cities)) -->
<!-- { -->

<!--   select<- c("car", "motorcycle", "walking", "cycle", "bus") -->

<!--   io[[cities[x]]]$trip_scen_sets$trip_mode[!io[[cities[x]]]$trip_scen_sets$trip_mode %in% select]<- "other" -->

<!--   dist_scen<- io[[cities[x]]]$trip_scen_sets %>% group_by(trip_mode, scenario) %>% summarise(sum(trip_distance)) -->
<!--   dist_scen<- as.data.frame (dist_scen) -->
<!--   names(dist_scen)[3]<-"distance" -->
<!--   dist_scen$distance<- round(dist_scen$distance, digits=0) -->
<!--     dist_scen<-spread(dist_scen, trip_mode, distance) -->
<!--   dist_scen$sum<-rowSums (dist_scen[2:(ncol(dist_scen))], na.rm = FALSE, dims = 1) -->
<!--   dist_scen_prop<- round(dist_scen[,2:(ncol(dist_scen))]*100/dist_scen$sum, digits=1) -->
<!--   dist_scen_prop<- cbind(dist_scen[,1], dist_scen_prop) -->

<!--   names(dist_scen_prop)[1]<-"Scenario" -->
<!--   dist_scen_prop$Scenario<- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen") -->
<!--   print(kable(dist_scen_prop, caption= cities[x])) -->
<!--   print(kable(dist_scen, caption= cities[x])) -->

<!-- } -->
<!-- ``` -->

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  # names(io[[cities[x]]]$outcomes$mmets)[5:10] <- c("Baseline","Walking",
  #                                                  "Bicycling", "Driving",
  #                                                  "Motorcycling", 
  #                                                  "Public Transport")
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets)
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - 4):n_col] <- scen_names
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:`Motorcycling`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) + geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly MMET", x = "Scenarios") + ylim(0, limit)
  print(y)

>>>>

input_parameter_file <- "InputParameters_v28.0.xlsx"
# scenario definition
scenario_name <- "GLOBAL"
reference_scenario <- 'Baseline'

@@

@@

print(kable(sl))
```

@@

co2_conc$Scenario <- scen_names

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets)
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - 4):n_col] <- scen_names

@@

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets)
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - 4):n_col] <- scen_names
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:`Motorcycling`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) + geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly MMET", x = "Scenarios") + ylim(0, limit)
  print(y)
